Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2022-04-27 article/draft.tex
cosmetic changes

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
\date{September 27, 2021}
\maketitle

>>>>

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, Sciences Po, m\'{e}dialab .}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{thero.heloise@gmail.com, Sciences Po, m\'{e}dialab.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, Sciences Po, m\'{e}dialab.}}
\date{September 27, 2021}
\maketitle
